The Radio Sky at Meter Wavelengths: $m$-Mode Analysis Imaging with the Owens Valley Long Wavelength Array

### 2017-02-22 paper.tex
add a paragraph on removing the amplitude of the sawtooth pattern

\todo{sawtooth pattern removal, does it affect phase???}

@@

\begin{figure*}[ht]
    \includegraphics[width=\textwidth, draft]{maps/rgb-map}
    \caption{three color map}
\end{figure*}

>>>>

Temperature fluctuations within the electronics shelter generate 0.1 dB sawtooth oscillations in the
analog gain. These oscillations occur with a variable 15 to 17 minute period. The amplitude of these
gain fluctuations is calibrated by smoothing the autocorrelation amplitudes on 45 minute timescales.
The ratio of the measured auto-correlation power to the smoothed auto-correlation power defines a
per-antenna amplitude correction that is then applied to the cross-correlations.

@@

\begin{figure*}[ht]
    \includegraphics[width=\textwidth]{maps/rgb-map-small}
    \caption{three color map}
\end{figure*}
